\documentclass[11pt]{article}
\usepackage{graphicx}
\setlength\parindent{0pt}
\usepackage{listings}
\usepackage{times}
\usepackage{color}


\title{Assignment 11}
\date{ 28/09/2014}
\begin{document}
\maketitle

\section*{Problem Statement}
Implementation of review comments submitted by customer and by lab teacher. Demonstrate learning of quantitative skills to implement comments in review 1. 
\section*{Objective}\
\begin{itemize}
\item To learn use of advance programming, documentation, presentation and communication tools.
\item To learn use to group discussions in problem solving.
\item To learn quantitative skills
\end{itemize}

\section*{Outcomes}\
\begin{itemize}
\item Ability to understand need of technical competence required for problem solving
\item Ability to understand the flaws in the current product and make changes according to the review.
\item Ability to understand the requirements of the client and work on it.
\end{itemize}

\section*{Theory}
Review comments:\\
At a glance, The client found certain aspects of the product which weren't up to his satisfaction. The GUI needed changes as it was not compelling enough. To implement this, We learnt CSS and incorporated it with the HTML files making the GUI more appreciable.\\
Another comment by the client when using the product was that there was a need to implement an alert box when an incorrect password was entered. This was incorporated using Javascript which gives an alert box for the same with the text "Incorrect Password/Username".\\
All the valuable inputs provided us by our client and respected teacher were taken into account and changes were made to satisfy these in order to preserve the functionality and the aesthetics of the product.
\section*{Conclusion}
Thus,we have taken into consideration the review given by the customer and made changes accordingly.
\end{document}